Splitting It Up: The \pkg{spduration} Split-Population Duration Regression Package for Time-varying Covariates

### 2017-06-24 R Journal/beger-hill-metternich-minhas-ward.tex
small updates

% !TeX root = RJwrapper.tex
\title{Splitting It Up: The \pkg{spduration} Split-Population Duration
Regression Package}
\author{by Andreas Beger, Daniel W. Hill, Jr., Nils. W. Metternich, Shahryar Minhas, and Michael D. Ward}

@@

\abstract{
We present an implementation of split-population duration regression in
the \CRANpkg{spduration} \citep{beger2016spduration} package for {\sf R} \citep{rstats2016} and an application to data on military
coups. The statistical model accounts for units that are immune to a
certain outcome and not part of the duration process the researcher is
primarily interested in. We provide insights that if immune units exist,
we can significantly increase the predictive performance compared to
standard duration models. The package includes estimation and several
post-estimation methods for split-population Weibull and Loglogistic
models.
}

@@

\address{Nils W. Metternich\\
  Department of Political Science\\
  School of Public Policy, University College London\\
  London\\
  United Kingdom\\
  \email{n.metternich@ucl.ac.uk}}

>>>>

% !TeX root = RJwrapper.tex
\title{Splitting It Up: The \pkg{spduration} Split-Population Duration
Regression Package for Time-varying Covariates}
\author{by Andreas Beger, Daniel W. Hill, Jr., Nils. W. Metternich, Shahryar Minhas, and Michael D. Ward}

@@

\abstract{
We present an implementation of split-population duration regression in
the \CRANpkg{spduration} \citep{beger2016spduration} package for {\sf R} \citep{rstats2016} that allows for time-varying covariates. The statistical model accounts for units that are immune to a
certain outcome and not part of the duration process the researcher is
primarily interested in. We provide insights that if immune units exist,
we can significantly increase the predictive performance compared to
standard duration models. The package includes estimation and several
post-estimation methods for split-population Weibull and Loglogistic
models. We provide an empirical application to data on military
coups.
}

@@

\address{Nils W. Metternich\\
  Department of Political Science\\
University College London\\
  London\\
  United Kingdom\\
  \email{n.metternich@ucl.ac.uk}\\
  Nils W. Metternich acknowledges support from the Economic and Social Research Council (ES/L011506/1)}
